FoRTE baseline

### 2019-07-23 analysis/paper/paper.Rmd
Update first results paragraph

Model projections of gross and net primary productivity, aboveground biomass, leaf area index, and functional diversity varied with both parameter value and model structure (Figure 2).
The ensemble means of all model configurations exhibited a similar trajectory of rapid growth in the first 15-20 years followed by a gradual decline throughout the rest of the simulation (with individual ensemble members sometimes undergoing sudden collapse in specific years).
However, the average rate of decline varied by model configuration.
Compared to models with a "closed" canopy (i.e. complete shading; no horizontal competition), models with a "finite" canopy predicted faster decline in net primary productivity and functional diversity.
This decline was most severe in configurations that combined the finite canopy and two-stream radiative transfer; in these configurations, a disproportionately large number of ensembles experienced complete ecosystem collapse over the course of the simulation, and the overwhelming fraction of ensemble members predicted near-zero Shannon diversity after 30 years. <!-- TODO Update this sentence -- the NPP is just super low -->
Besides this specific configuration, which consistently under-predicted observed net primary productivity at UMBS, the remaining model configurations had ensemble mean net primary productivity values that were very close to the values observed at UMBS.

Patterns in leaf area index were somewhat distinct from patterns in productivity and diversity.
While model configurations with finite canopy and two-stream radiative transfer again predicted the lowest leaf area index on average, model configurations with finite canopy and multiple-scatter predicted the _highest_ leaf area index on average (though this was skewed by a relatively small number of extremely high-LAI simulations).
The latter configurations also had the largest number of ensemble members that fell within the observed distribution of leaf area index; meanwhile, every model configuration predicted an ensemble mean leaf area index at the end of the simulation that was significantly below the UMBS observations.

>>>>

Model projections of gross and net primary productivity, aboveground biomass, leaf area index, and functional diversity varied with both parameter value and model structure (Figure 2).
One model configuration -- finite canopy radius, two-stream radiative transfer, and plastic traits -- failed to grow at all, regardless of parameter combinations, and a similar configuration with static traits showed much less growth than any other model configurations.
The remaining configurations all exhibited a similar trajectory of rapid growth in the first 15-20 years followed by a gradual decline to a lower, stable value around 1975 (with individual ensemble members sometimes undergoing sudden collapse in specific years).
The ensemble mean ecosystem state of most model confugrations had net primary productivity very close to that observed at UMBS, but generally much lower leaf area index.
However, the ensemble spread around the mean was large -- across all configurations (except the finite canopy - two-stream radiative transfer cases), the spread in net primary productivity was from zero to several times higher than the observed.
Ensemble variance in leaf area index was lower on average but, in some case (e.g. finite canopy, multiple-scatter radiative transfer, static traits) was over an order of magnitude.
The predicted Shannon diversity index of plant functional types was, on average, higher in simulations when the canopy architecture was finite rather than closed.
